Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2021-09-09 summary_minh_edited.tex
cleaned things up a bit more

In contrast to Block Models, neither RDPGs nor GRDPGs inherently
specify distinct communities.  However, one can easily impose
community structure by assuming that the latent positions lie in
distinct clusters.  Hence, it is not surprising that Block Models can
be studied by reformulating them as RDPGs or GRDPGs.  For example, an
assortative SBM (an SBM for which $P$ is positive semidefinite) is
equivalent to an RDPG for which all vertices in the same community
correspond to the same latent position vector.
Likewise, the DCBM is equivalent to an RDPG for which all vertices in
the same community correspond to latent position vectors that lie on a
straight line. %(\cite{lyzinski2014, rubindelanchy2017statistical}).

@@

\begin{remark}
  \label{rem:pabm_view2}
% Let $P \in [0, 1]^{n \times n}$ be a symmetric edge probability matrix for a
% graph $G = (V, E)$ with adjacency matrix $A$ 
% such that $A \sim \mathrm{Bernoulli}(P)$.
% Let each vertex have a community label between $1$ and $K$.
% Then $G$ is drawn from a Popularity Adjusted Block Model if
In a PABM, each vertex $i$ has $K$ popularity parameters 
$\lambda_{i1}, \dots, \lambda_{iK}$, that describe its affinity
toward each of the $K$ communities. % , i.e., vertex $i$ has popularity parameters
% $\lambda_{i1}, ..., \lambda_{iK}$, and  $P_{ij} = \lambda_{i z_j}
% \lambda_{j z_i}$ for all $i \leq j$. 
Another view of a PABM is as follows.
Let $\tilde{P}$ be the matrix obtained by permuting the rows and
columns of $P$ so that the vertices are arranged according to
increasing values of the community assignments $z_i \in
\{1,2,\dots,K\}$. Denote by $\tilde{P}^{(k \ell)}$ the $n_k \times n_{\ell}$
submatrix of $\tilde{P}$ corresponding to the
edge probabilities between vertices in communities
$k$ and $\ell$. Here $n_k = |\{ i \colon z_i = k\}|$ is the number of
vertices assigned to community $k$, for $k = 1,2\dots,K$.
Note that $\tilde{P}^{(k \ell)} = (\tilde{P}^{(\ell k)})^\top$. Next
let $\lambda^{(k \ell)} = \{\lambda_{i \ell} \colon z_i = k\} \in
\mathbb{R}^{n_k}$; the elements of $\lambda^{(k \ell)}$ are the affinity parameters toward the $\ell$th community of
all vertices in the $k^{th}$ community. Define $\lambda^{(\ell k)}$
analogously. Then each block $\tilde{P}^{(k \ell)}$ can be written as the outer product of two vectors:
\begin{equation} \label{eq:pabm}
  \tilde{P}^{(k \ell)} = \rho_n \lambda^{(k \ell)} (\lambda^{(\ell k)})^{\top}.
\end{equation}
% for a set of $K^2$ popularity vectors 
% $\{\lambda^{(st)}\}_{1 \leq s \leq K, 1 \leq t \leq K}$ where each
% $\lambda^{(st)}$ is a column vector of dimension $n_s$.
% . Then a graph $G$
% is drawn from a PABM with parameters
% $\{\lambda^{(st)}\}$ if its adjacency matrix $A$
% satisfies $A \sim \mathrm{BernoulliGraph}(P)$.
We will henceforth use the notation \(A \sim \PABM(\{\lambda^{(k
  \ell)}\}_K, \rho_n)\) to denote
a random adjacency matrix \(A\) drawn from a PABM with $K$ communities, popularity parameters
\(\{\lambda^{(k \ell)}\}\) and sparsity parameter $\rho_n$.
\end{remark}

@@

\begin{definition}[Generalized Random Dot Product Graph]
\label{grdpg}
Let $p \geq 1$ and $q \geq 0$ be integers. Define $I_{p,q}$ as the
block diagonal matrix $I_{p,q} = \Bigl[\begin{smallmatrix} I_{p} & 0
  \\ 0 & - I_{q} \end{smallmatrix} \Bigr]$ where $I_{p}$ and $I_{q}$
are the identity matrices of dimensions $p \times p$ and $q \times q$
respectively. Next let $\mathcal{X}$ be a subset of $\mathbb{R}^{d}$
such that $x^{\top} I_{p,q} y \in [0,1]$ for all $x,y \in
\mathcal{X}$. Let $X = \bigl[x_1 \mid \cdots \mid x_n\bigr]^{\top}$ be
a $n \times d$ matrix with rows $x_i \in \mathcal{X}$. A graph $G$
with adjacency matrix $A$ is said to be a generalized random dot
product graph with latent positions $X$, sparsity parameter $\rho_n
\in (0,1]$
and signature $(p,q)$ if $A \sim \BG(P)$ where the edge probability
matrix $P$ is given
by $P = \rho_n X I_{p,q} X^{\top}$, i.e., the entries of $P$ are of
the form
$$P_{ij} = \rho_n x_i^{\top} I_{p,q} x_j.$$
% Let graph $G = (V, E)$ be drawn as $A \sim \BG(P)$ for some symmetric $P \in
% [0,1]^{n \times n}$. 
% If there exists a data matrix $X \in \mathbb{R}^{n \times d}$ such that
% \begin{equation} \label{eq:grdpg}
%   P = X I_{p,q} X^\top
% \end{equation}
% for some $d, p, q \in \mathbb{N}$ and $p + q = d$, then
% $G$ is drawn from the Generalized Random Dot Product Graph 
% with latent positions $x_1, ..., x_n \in \mathbb{R}^d$ and signature $(p, q)$.
\end{definition}
We will use the notation \(A \sim \GRDPG_{p,q}(X;\rho_n)\) to denote a random
adjacency matrix \(A\) drawn from latent positions \(X\), sparsity
parameter $\rho_n$ and signature
\((p, q)\). % If instead of fixed latent positions, 
% they are drawn $X_1, ..., X_n \iid F$, 
% we denote the GRDPG as $(A, X) \sim \GRDPG_{p,q}(F, n)$.
\begin{remark}
  \label{rem:ase}
We can use Adjacency Spectral Embedding (ASE) 
\citep{doi:10.1080/01621459.2012.699795} to recover the latent vectors of a GRDPG. 
This procedure consists of taking the spectral decomposition of $A$ 
(or $P$ if available) and choosing the $p$ most positive and $q$ most negative
eigenvalues and their corresponding eigenvectors 
to construct the embedding $\hat{Z} = V |D|^{1/2}$. 
\end{remark}

@@

We previously stated in Theorem~\ref{theorem2} one possible set of latent positions that result in
the edge probability matrix of a PABM, namely
\(P = \tilde{\Pi} (XU) I_{p, q}
(XU)^\top \tilde{\Pi}^{\top}\) where $X$ is block diagonal and
$\tilde{\Pi}$ is a permutation matrix.  
Furthermore, the explicit form of \(XU\) represents points in \(\mathbb{R}^{K^2}\)
such that points within each community lie on \(K\)-dimensional
orthogonal subspaces, i.e. $\langle U^{\top} x_i, U^{\top} x_j \rangle = 0$ whenever $z_i \not = z_j$. 
Thus if
we have (or can estimate) \(XU\) directly, then both the community
detection and parameter identification problem are trivial because \(U\)
is orthonormal and fixed for each value of \(K\). 
However, direct
identification or estimation of \(XU\) is possibly difficult 
due to the non-identifiability of $XU$ (see Remark~\ref{rem:non_identifiable}).
when we are given only $P$. % of the latent
% positions of a GRDPG.  
% due to the
% non-identifiability of \(XU\) when we are only given $P$, 
% direct
% identification or estimation of \(XU\) is possibly difficult 
% if we are only given $P$. 
% (\cite{rubindelanchy2017statistical}).
More specifically, suppose we find a matrix $Y \in
\mathbb{R}^{n \times K^2}$
such that \(P = Y I_{p, q} Y^\top\). Then it is generally the case that
we  \( Y = \tilde{\Pi} XU Q \) for some indefinite orthogonal matrix
$Q \in \mathbb{O}(p,q)$. %  as there is no
% general matrix decomposition that yield 
% The explicit form of \(XU\) represents points in \(\mathbb{R}^{K^2}\)
% such that points within each community lie on \(K\)-dimensional
% orthogonal subspaces. Multiplication by \(Q \in \mathbb{O}(p, q)\)
% removes the orthogonality property but retains the property that each
% community is represented by a \(K\)-dimensional subspace. 
% However, because $\tilde{\Pi}$ is unknown (indeed, if we know $\tilde{\Pi}$
% then we also know the community labels), 
% Therefore, even if we
% start with the true but unknown edge probability matrix $P$ we
% will not be able to recover the latent positions \(XU\).
However since \(Q\) is not necessarily an
orthogonal matrix and hence, if $y_i$ denote the $i^{th}$ row of $Y$, 
then $\langle U^{\top} x_i, U^{\top} x_j \rangle
\neq \langle y_i, y_j \rangle$.
This prevents us from transferring the orthogonality property of
\(XU\) directly to $Y$.

@@

We also note that unlike the MLE-based method
\citep{307cbeb9b1be48299388437423d94bf1}, the ASE method in
Algorithm~\ref{alg:param_est} can be trivially modified so as to not
require the community labels if we are only interested in 
estimating $P$. More specifically we first compute the ASE
$\hat{Z}$ of $A$ (see Remark~\ref{rem:ase}) and then compute $\hat{P}
= \hat{Z} I_{p,q} \hat{Z}^{\top}$. The resulting estimate $\hat{P}$
will have the same convergence rate as that given in Eq.~(\ref{eq:conv_prob}).
% we obtain by
% combining the popularity vectors outputted by
% Algorithm~\ref{alg:param_est} is asymptotically
% equivalent to using the full ASE of $A$ to reconstruct the edge
% probability matrix.

@@

% (We can also note that
% the SVD of \(P^{(lk)} = \sigma_{kl}^2 v^{(kl)} (u^{(kl)})^\top\), i.e.,
% \(\sigma_{kl} = \sigma_{lk}\), \(u^{(kl)} = v^{(lk)}\), and
% \(v^{(kl)} = u^{(lk)}\).)\\
Next consider the Hermitian dilation

@@

\[M^{(k \ell)} = 
\begin{bmatrix} u^{(k \ell)} & -u^{(k \ell)} \\ v^{(k \ell)} & v^{(k \ell)} \end{bmatrix} \times 
\begin{bmatrix} \sigma^2_{kl} & 0 \\ 0 & -\sigma^2_{kl} \end{bmatrix} \times
\begin{bmatrix} u^{(k \ell)} & -u^{(k \ell)} \\ v^{(k \ell)} & v^{(k \ell)} \end{bmatrix}^\top\]
Thus treating \(M^{(k \ell)}\) as the edge probability matrix of a GRDPG, we
have latent positions in \(\mathbb{R}^2\) given by the $(n_k + n_{\ell}) \times 2$ matrix
\[\Lambda^{(k \ell)} = \begin{bmatrix} 
  \sigma_{k \ell} u^{(k \ell)} & \sigma_{k \ell} u^{(k \ell)} \\ 
  \sigma_{k \ell} v^{(k \ell)} & -\sigma_{k \ell} v^{(k \ell)} 
\end{bmatrix} = 
\begin{bmatrix} 
  \lambda^{(k \ell)} & \lambda^{(k \ell)} \\ 
  \lambda^{( \ell k)} & -\lambda^{( \ell k)} 
\end{bmatrix}.\]
Now consider
\[\hat{M}^{(k \ell)} = \begin{bmatrix} 0 & A^{(k \ell)} \\ A^{(\ell k)} & 0 \end{bmatrix}\]
% Then \(\hat{M}^{(kl)} = M^{(kl)} + E'\) where

% \[E' = \begin{bmatrix} 0 & E \\ E^\top & 0 \end{bmatrix}\]

% and \(E\) is the \(n_k \times n_\ell\) matrix of independent noise (to
% generate the Bernoulli entries in \(A^{(kl)}\).\\
We can then view \(\hat{M}^{(k \ell)}\) as an adjacency matrix drawn from
the edge probabilities matrix \(M^{(k \ell)}\). Now suppose that the adjacency spectral
embedding of $\hat{M}^{(k \ell)}$ is represented as the $(n_k +
n_{\ell}) \times 2$ matrix
\[\hat{\Lambda}^{(k \ell)} = \begin{bmatrix} 
  \hat{\lambda}^{(k \ell)} & \hat{\lambda}^{(k \ell)} \\ 
  \hat{\lambda}^{(\ell k)} & -\hat{\lambda}^{(\ell k)} 
\end{bmatrix}\]
where each \(\hat{\lambda}^{(k \ell)}\) is defined as in Algorithm 3. Then
by Theorem 5 of \citet{rubindelanchy2017statistical}, there
exists an indefinite orthogonal transformation $W^{*}$ such that,  with
high probability,
$$\max_{i} |W^{*} \hat{\Lambda}_{i}^{(k \ell)} - \Lambda_{i}^{(k \ell)} \| =
O\Bigl(\frac{\log (n_k + n_{\ell})}{\sqrt{n_k + n_{\ell}}}\Bigr)$$
with high probability. Here $\Lambda_{i}^{(k \ell)}$ and
$\hat{\Lambda}_i^{(k \ell)}$ denote the $i$th rows of $\Lambda^{(k
  \ell)}$ and $\hat{\Lambda}^{(k \ell)}$, respectively. 
% approximates the latent positions of \(M^{(kl)}\) up to indefinite
% orthogonal transformation by the rate given in Theorem 5 of
% \citet{rubindelanchy2017statistical}.\\
Furthermore, by looking at the proof of Theorem~5 in
\citep{rubindelanchy2017statistical}, we see that $W^{*}$ is also
blocks diagonal with $2$ blocks where the positive eigenvalues of $M^{(k \ell)}$
forming a block and the negative eigenvalues of $M^{(k \ell)}$ forming
the remaining block. % \(U^\top \hat{U}\). 
Because $M^{(k \ell)}$ has one positive eigenvalue and one negative
eigenvalue, we see that $W^{*}$ is necessarily of the form $W^{*}
= \Bigl[\begin{smallmatrix} 1 & 0 \\ 0 & - 1\end{smallmatrix}\Bigr]$
% \((1, 1)\), and \(U^\top \hat{U}\) is block
% diagonal, resulting in \(W_* \stackrel{a.s.}{\to} I\). 
Using this form for $W^{*}$, we obtain
$$\max\{\|\hat{\lambda}^{(k \ell)} - \lambda^{(k \ell)}\|_{\infty},
\|\hat{\lambda}^{(\ell k)} - \lambda^{(\ell k)}\|_{\infty}\}  =
O\Bigl(\frac{\log(n_k + n_{\ell})}{\sqrt{n_k + n_{\ell}}}\Bigr)$$
with high probability. Combining this bound with the bound for
$\|\hat{\lambda}^{(kk)} - \lambda^{(kk)}\|_{\infty}$ given above
yields Eq.~\eqref{eq:thm6} in Theorem~\ref{theorem6}. 
\end{proof}
\end{document}

>>>>

In contrast to Block Models, neither RDPGs nor GRDPGs inherently
specify distinct communities.  However, one can easily impose
community structure by assuming that the latent positions lie in
distinct clusters.  Hence, it is not surprising that Block Models can
be studied by reformulating them as RDPGs or GRDPGs.  For example, an
assortative SBM (an SBM for which $P$ is positive semidefinite) is
equivalent to an RDPG for which all vertices in the same community
correspond to the same latent position vector.
Likewise, the DCBM is equivalent to an RDPG for which all vertices in
the same community correspond to latent position vectors that lie on a
straight line.

@@

\begin{remark}
  \label{rem:pabm_view2}
In a PABM, each vertex $i$ has $K$ popularity parameters 
$\lambda_{i1}, \dots, \lambda_{iK}$, that describe its affinity
toward each of the $K$ communities. 
Another view of a PABM is as follows.
Let $\tilde{P}$ be the matrix obtained by permuting the rows and
columns of $P$ so that the vertices are arranged according to
increasing values of the community assignments $z_i \in
\{1,2,\dots,K\}$. Denote by $\tilde{P}^{(k \ell)}$ the $n_k \times n_{\ell}$
submatrix of $\tilde{P}$ corresponding to the
edge probabilities between vertices in communities
$k$ and $\ell$. Here $n_k = |\{ i \colon z_i = k\}|$ is the number of
vertices assigned to community $k$, for $k = 1,2\dots,K$.
Note that $\tilde{P}^{(k \ell)} = (\tilde{P}^{(\ell k)})^\top$. Next
let $\lambda^{(k \ell)} = \{\lambda_{i \ell} \colon z_i = k\} \in
\mathbb{R}^{n_k}$; the elements of $\lambda^{(k \ell)}$ are the affinity parameters toward the $\ell$th community of
all vertices in the $k^{th}$ community. Define $\lambda^{(\ell k)}$
analogously. Then each block $\tilde{P}^{(k \ell)}$ can be written as the outer product of two vectors:
\begin{equation} \label{eq:pabm}
  \tilde{P}^{(k \ell)} = \rho_n \lambda^{(k \ell)} (\lambda^{(\ell k)})^{\top}.
\end{equation}

We will henceforth use the notation \(A \sim \PABM(\{\lambda^{(k
  \ell)}\}_K, \rho_n)\) to denote
a random adjacency matrix \(A\) drawn from a PABM with $K$ communities, popularity parameters
\(\{\lambda^{(k \ell)}\}\) and sparsity parameter $\rho_n$.
\end{remark}

@@

\begin{definition}[Generalized Random Dot Product Graph]
\label{grdpg}
Let $p \geq 1$ and $q \geq 0$ be integers. Define $I_{p,q}$ as the
block diagonal matrix $I_{p,q} = \Bigl[\begin{smallmatrix} I_{p} & 0
  \\ 0 & - I_{q} \end{smallmatrix} \Bigr]$ where $I_{p}$ and $I_{q}$
are the identity matrices of dimensions $p \times p$ and $q \times q$
respectively. Next let $\mathcal{X}$ be a subset of $\mathbb{R}^{d}$
such that $x^{\top} I_{p,q} y \in [0,1]$ for all $x,y \in
\mathcal{X}$. Let $X = \bigl[x_1 \mid \cdots \mid x_n\bigr]^{\top}$ be
a $n \times d$ matrix with rows $x_i \in \mathcal{X}$. A graph $G$
with adjacency matrix $A$ is said to be a generalized random dot
product graph with latent positions $X$, sparsity parameter $\rho_n
\in (0,1]$
and signature $(p,q)$ if $A \sim \BG(P)$ where the edge probability
matrix $P$ is given
by $P = \rho_n X I_{p,q} X^{\top}$, i.e., the entries of $P$ are of
the form

$$P_{ij} = \rho_n x_i^{\top} I_{p,q} x_j.$$

\end{definition}
We will use the notation \(A \sim \GRDPG_{p,q}(X;\rho_n)\) to denote a random
adjacency matrix \(A\) drawn from latent positions \(X\), sparsity
parameter $\rho_n$ and signature
\((p, q)\).

\begin{remark}
  \label{rem:ase}
We can use Adjacency Spectral Embedding (ASE) 
\citep{doi:10.1080/01621459.2012.699795} to recover the latent vectors of a GRDPG. 
This procedure consists of taking the spectral decomposition of $A$ 
(or $P$ if available) and choosing the $p$ most positive and $q$ most negative
eigenvalues and their corresponding eigenvectors 
to construct the embedding $\hat{Z} = V |D|^{1/2}$. 
\end{remark}

@@

We previously stated in Theorem~\ref{theorem2} one possible set of latent positions that result in
the edge probability matrix of a PABM, namely
\(P = \tilde{\Pi} (XU) I_{p, q}
(XU)^\top \tilde{\Pi}^{\top}\) where $X$ is block diagonal and
$\tilde{\Pi}$ is a permutation matrix.  
Furthermore, the explicit form of \(XU\) represents points in \(\mathbb{R}^{K^2}\)
such that points within each community lie on \(K\)-dimensional
orthogonal subspaces, i.e. $\langle U^{\top} x_i, U^{\top} x_j \rangle = 0$ whenever $z_i \not = z_j$. 
Thus if
we have (or can estimate) \(XU\) directly, then both the community
detection and parameter identification problem are trivial because \(U\)
is orthonormal and fixed for each value of \(K\). 
However, direct
identification or estimation of \(XU\) is possibly difficult 
due to the non-identifiability of $XU$ (see Remark~\ref{rem:non_identifiable})
when we are given only $P$. 
More specifically, suppose we find a matrix $Y \in
\mathbb{R}^{n \times K^2}$
such that \(P = Y I_{p, q} Y^\top\). Then it is generally the case that
we  \( Y = \tilde{\Pi} XU Q \) for some indefinite orthogonal matrix
$Q \in \mathbb{O}(p,q)$. 
However since \(Q\) is not necessarily an
orthogonal matrix and hence, if $y_i$ denote the $i^{th}$ row of $Y$, 
then $\langle U^{\top} x_i, U^{\top} x_j \rangle
\neq \langle y_i, y_j \rangle$.
This prevents us from transferring the orthogonality property of
\(XU\) directly to $Y$.

@@

We also note that unlike the MLE-based method
\citep{307cbeb9b1be48299388437423d94bf1}, the ASE method in
Algorithm~\ref{alg:param_est} can be trivially modified so as to not
require the community labels if we are only interested in 
estimating $P$. More specifically we first compute the ASE
$\hat{Z}$ of $A$ (see Remark~\ref{rem:ase}) and then compute $\hat{P}
= \hat{Z} I_{p,q} \hat{Z}^{\top}$. The resulting estimate $\hat{P}$
will have the same convergence rate as that given in Eq.~(\ref{eq:conv_prob}).

@@

Next consider the Hermitian dilation

@@

\[M^{(k \ell)} = 
\begin{bmatrix} u^{(k \ell)} & -u^{(k \ell)} \\ v^{(k \ell)} & v^{(k \ell)} \end{bmatrix} \times 
\begin{bmatrix} \sigma^2_{kl} & 0 \\ 0 & -\sigma^2_{kl} \end{bmatrix} \times
\begin{bmatrix} u^{(k \ell)} & -u^{(k \ell)} \\ v^{(k \ell)} & v^{(k \ell)} \end{bmatrix}^\top\]
Thus treating \(M^{(k \ell)}\) as the edge probability matrix of a GRDPG, we
have latent positions in \(\mathbb{R}^2\) given by the $(n_k + n_{\ell}) \times 2$ matrix
\[\Lambda^{(k \ell)} = \begin{bmatrix} 
  \sigma_{k \ell} u^{(k \ell)} & \sigma_{k \ell} u^{(k \ell)} \\ 
  \sigma_{k \ell} v^{(k \ell)} & -\sigma_{k \ell} v^{(k \ell)} 
\end{bmatrix} = 
\begin{bmatrix} 
  \lambda^{(k \ell)} & \lambda^{(k \ell)} \\ 
  \lambda^{( \ell k)} & -\lambda^{( \ell k)} 
\end{bmatrix}.\]
Now consider
\[\hat{M}^{(k \ell)} = \begin{bmatrix} 0 & A^{(k \ell)} \\ A^{(\ell k)} & 0 \end{bmatrix}\]

We can then view \(\hat{M}^{(k \ell)}\) as an adjacency matrix drawn from
the edge probabilities matrix \(M^{(k \ell)}\). Now suppose that the adjacency spectral
embedding of $\hat{M}^{(k \ell)}$ is represented as the $(n_k +
n_{\ell}) \times 2$ matrix
\[\hat{\Lambda}^{(k \ell)} = \begin{bmatrix} 
  \hat{\lambda}^{(k \ell)} & \hat{\lambda}^{(k \ell)} \\ 
  \hat{\lambda}^{(\ell k)} & -\hat{\lambda}^{(\ell k)} 
\end{bmatrix}\]
where each \(\hat{\lambda}^{(k \ell)}\) is defined as in Algorithm 3. Then
by Theorem 5 of \citet{rubindelanchy2017statistical}, there
exists an indefinite orthogonal transformation $W^{*}$ such that,  with
high probability,
$$\max_{i} |W^{*} \hat{\Lambda}_{i}^{(k \ell)} - \Lambda_{i}^{(k \ell)} \| =
O\Bigl(\frac{\log (n_k + n_{\ell})}{\sqrt{n_k + n_{\ell}}}\Bigr)$$
with high probability. Here $\Lambda_{i}^{(k \ell)}$ and
$\hat{\Lambda}_i^{(k \ell)}$ denote the $i$th rows of $\Lambda^{(k
  \ell)}$ and $\hat{\Lambda}^{(k \ell)}$, respectively.

Furthermore, by looking at the proof of Theorem~5 in
\citep{rubindelanchy2017statistical}, we see that $W^{*}$ is also
blocks diagonal with $2$ blocks where the positive eigenvalues of $M^{(k \ell)}$
forming a block and the negative eigenvalues of $M^{(k \ell)}$ forming
the remaining block. 
Because $M^{(k \ell)}$ has one positive eigenvalue and one negative
eigenvalue, we see that $W^{*}$ is necessarily of the form $W^{*}
= \Bigl[\begin{smallmatrix} 1 & 0 \\ 0 & - 1\end{smallmatrix}\Bigr]$
Using this form for $W^{*}$, we obtain
$$\max\{\|\hat{\lambda}^{(k \ell)} - \lambda^{(k \ell)}\|_{\infty},
\|\hat{\lambda}^{(\ell k)} - \lambda^{(\ell k)}\|_{\infty}\}  =
O\Bigl(\frac{\log(n_k + n_{\ell})}{\sqrt{n_k + n_{\ell}}}\Bigr)$$
with high probability. Combining this bound with the bound for
$\|\hat{\lambda}^{(kk)} - \lambda^{(kk)}\|_{\infty}$ given above
yields Eq.~\eqref{eq:thm6} in Theorem~\ref{theorem6}. 
\end{proof}
\end{document}
